\setlength{\parindent}{0em}
\section*{Abstract}
This report explains the main topics we learned during our two-month internship on Group Theory, a central topic in Abstract Algebra.  It includes important topics such as groups, subgroups, cyclic groups, permutation groups, homomorphisms, external direct products, normal subgroups, and factor groups. The report also includes several important theorems and examples to help to explain the topics more clearly. We studied these using the book \textit{Contemporary Abstract Algebra} by Joseph A. Gallian and solved many exercises from it. Some of those exercises are also explained in this report.

Along with reading and solving exercises, we also focused on how computers can be used in the field of Group theory. Computers do many things faster and easier, so using them in group theory can help us explore more advanced topics in the future. 

As part of this, I wrote several programs related to group theory using Python. Some were suggested by my guide, Prof. Krishna Hanumanthu, and some were based on exercises from the book.  The program I wrote includes:
\begin{itemize}
    \item Finding the inverse, order, and Cayley table of the $U(n)$ and $\mathbb{Z}_n$ groups.
    \item Finding the order of the group $GL(2, \mathbb{Z}_p)$, and also the inverse and order of its elements.
    \item Counting the number of elements in each cycle type in the $S_n$ group.
    \item Finding the order and the Cayley table of the $\mathbb{Z}_m \oplus \mathbb{Z}_n$ group.
\end{itemize}

The code for these programs can be found at the following link:
\begin{center}
    \url{https://github.com/shivam-raj12/Internship-Final-Report}
\end{center}